BIP Architectures and Open pNets

### 2019-01-23 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) clean-up, including one of the properties in Example 1.

\begin{definition}[Component semantics]
  \label{defn:comp:semantics}
  The \emph{open semantics} of a component $B = \tuple{Q, q^0, V,
  \val{0}{}, P, \export, \goesto{}}$ is given by the LTS denoted $\semopen{B} = \tuple{S,
  s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
  \tuple{q^0, \val{0}{}}$ and $\goesto{}$ is the minimal transition
  relation satisfying the rule
  %
  \begin{equation}
    \label{eq:comp:semantics}
    \infer{
      q \goesto{a, g, u} q'
      \and
      \val{}{} \models g
      \and
      \val[\primeit]{}{} = \tilde{\val{}{}}[u]
      \and
      \valdiff{\val{}{}}{\tilde{\val{}{}}} \subseteq \export(a)
    }{
      (q, \val{}{}) \goesto{a,\tilde{\val{}{}}} (q', \val[\primeit]{}{})
    }
    \,.
  \end{equation}
  %
  \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
  \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
  $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
  only the reachable states of $\semopen{B}$.}
\end{definition}

@@

\begin{example}
  The architecture in \fig{schema:ArchFailure:BIP} enforces the
  following properties:
  \begin{enumerate}
  \item There is always a possibility to reset the system after a
    failure:
    \begin{equation}
      \label{eq:prop:reset:can}
      \AG (\PortFail \rightarrow \EF \PortReset).
    \end{equation}
  \item Whenever a reset is requested, it will eventually be
    effectuated:
    \begin{equation}
      \label{eq:prop:reset:will}
      \AG (\PortAsk \rightarrow \AF \PortReset).
    \end{equation}
  \item As long as no failure has occured, the $z$ variable of the
    $\NameTimer$ component has the value $\topinterval$:
    \begin{equation}
      \label{eq:prop:z:top}
      \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
      \AG \bigl(
      \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
      \bigr).
    \end{equation}
  \item A timeout can only occur within the specified delay after
    a failure:
    \begin{multline}
      \label{eq:prop:to:delay}
      \forall T_0, T_1 \in \sZ,\
      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
      \\
      \AW[]{\bigl((\PortTOC \land \NameTimer.t = T_1) \rightarrow
        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
      }{
        (\PortReset \lor \PortResume)
      }\Big),
    \end{multline}
    where $T_0$ and $T_1$ are integer parameters.  (The formula
    holds with the universal quantification over $T_0$ and $T_1$
    due to the fact that their individual values only appear in
    the left-hand sides of the two implications.)
  \end{enumerate}
\end{example}

>>>>

\begin{definition}[Component semantics]
  \label{defn:comp:semantics}
  The \emph{open semantics} of a component $B = \tuple{Q, q^0, V,
  \val{0}{}, P, \export, \goesto{}}$ is given by the LTS denoted $\semopen{B} = \tuple{S,
  s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
  \tuple{q^0, \val{0}{}}$ and $\goesto{}$ is the minimal transition
  relation satisfying the rule
  %
  \begin{equation}
    \label{eq:comp:semantics}
    \infer{
      q \goesto{a, g, u} q'
      \and
      \val{}{} \models g
      \and
      \val[\primeit]{}{} = \tilde{\val{}{}}[u]
      \and
      \valdiff{\val{}{}}{\tilde{\val{}{}}} \subseteq \export(a)
    }{
      (q, \val{}{}) \goesto{a,\tilde{\val{}{}}} (q', \val[\primeit]{}{})
    }
    \,.
  \end{equation}
  %
  %% \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
  %% \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
  %% $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
  %% only the reachable states of $\semopen{B}$.}
\end{definition}

@@

\begin{example}
  The architecture in \fig{schema:ArchFailure:BIP} enforces the
  following properties:
  \begin{enumerate}
  \item There is always a possibility to reset the system after a
    failure:
    \begin{equation}
      \label{eq:prop:reset:can}
      \AG (\PortFail \rightarrow \EF \PortReset).
    \end{equation}
  \item Whenever a reset is requested, it will eventually be
    effectuated:
    \begin{equation}
      \label{eq:prop:reset:will}
      \AG (\PortAsk \rightarrow \AF \PortReset).
    \end{equation}
  \item As long as no failure has occured, the $z$ variable of the
    $\NameTimer$ component has the value $\topinterval$:
    \begin{equation}
      \label{eq:prop:z:top}
      \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
      \AG \bigl(
      \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
      \bigr).
    \end{equation}
  \item A reset can only be requested within the specified delay after
    a failure:
    \begin{multline}
      \label{eq:prop:to:delay}
      \forall T_0, T_1 \in \sZ,\
      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
      \\
      \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
      }{
        (\PortReset \lor \PortResume)
      }\Big),
    \end{multline}
    where $T_0$ and $T_1$ are integer parameters.  (The formula
    holds with the universal quantification over $T_0$ and $T_1$
    due to the fact that their individual values only appear in
    the left-hand sides of the two implications.)
  \end{enumerate}
\end{example}
